Spec2Fab: A Graph-Based Framework for Fabricating Fabrication Algorithms

### 2012-12-20 paper.tex
interrupted

\subsection{Tuners}
\note{Desai: can you write this section, I don't know the details}
\subsection{Tuning the Reducer Network}

\subsection{Tuner Network}
\note{Desai: also this section :) }

>>>>

\subsection{Tuners}
\note{Desai: can you write this section, I don't know the details.

First pass: write down my ideas conversationally.
}

Tuners are interfaces between the Reducer Network and generic optimization algorithms.
A tuner can be attached to a node in the reducer graph.
When a tuner is attached to a node in the reducer graph, it can tune
all the free parameters in the subtree rooted at that node.
\subsection{Tuning a Reducer Node}
The tuner queries its node for information about the search space such as
number of free variables, variable types and bounds from the Reducer Network.
In addition, the tuner will set up call-back functions for error computation.

\subsection{Tuner Network}
\note{Desai: also this section :) }
In many fabrication problems, there are local dependencies between
different sub-trees. One simplest example is surface texture dithering
using error-diffusion. To account for such dependencies, we allow
tuners to share information according to a graph structure.
If two tuners share an edge, they can share information.
The network structure is specified by users.
